---
title: "Analyses"
output:
  html_document: default
  word_document: default
date: "2023-06-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
#Library:
```{r, warning=FALSE}

library(mice)
library(miceadds)
library(tidyverse)
library(haven)
library(dplyr)
library(psych)
library(ggplot2)
library(viridis)
library(hrbrthemes)
library(kableExtra)
library(forcats)
library(frequency)
library(interactions)
library(corrplot)
library(effsize)
library(kableExtra)
library(gtsummary)


school <- read.csv("database.csv")
school <- school %>%
  select(-X)

```

```{r load.rdata2}

elfe_mids <- load.Rdata2("ALL_elfe_ecole_imp/ALL_elfe_ecole_imp.Rdata", path=getwd())

```


#1/ Descriptive stats (table S3)

```{r results = 'asis'}

library(arsenal)

tab1 <- tableby(Sex ~ meduc_5y + feduc_5y + A5_TOTREVEN + A3_TOTREVEN + scorenum6 + scorenum4 + scorelit6 + scorelit4 + GA + GFO, data = school, control = tableby.control(numeric.stats = c("Nmiss", "meansd",  "medianq1q3"), test = F) )

summary(tab1, digits=2)



```


Dataset of children with a numeracy score in 1st grade
```{r}
test  <- complete(elfe_mids,"long",include=T)
test <- test[!is.na(test$scorenum6),]
elfe_mids_scorenum6 <- as.mids(test, .id="row")
```


#2/ Cohen d : 
```{r results = 'asis'}

#Cohen_6_num 
effsize::cohen.d(data=school, scorenum6 ~ Sex, na.rm = T)
# Cohen_4_num 
effsize::cohen.d(data=school, scorenum4 ~ Sex, na.rm = T)
# Cohen_6_lit 
effsize::cohen.d(data=school, scorelit6 ~ Sex, na.rm = T)
# Cohen_4_lit 
effsize::cohen.d(data= school, scorelit4 ~ Sex, na.rm = T)

```

Cohens'd difference in GFO and GA between boys and girls

```{r}

effsize::cohen.d(elfe_mids_scorenum6$data$GFO~elfe_mids_scorenum6$data$sexe)
effsize::cohen.d(elfe_mids_scorenum6$data$GA~elfe_mids_scorenum6$data$sexe)
```



# Figure 1 : GFO and GA distributions 

```{r}
df_long <- elfe_mids_scorenum6$data %>%
  pivot_longer(cols = c(GA, GFO), 
               names_to = "Type",
               values_to = "Value")

df_long$Type[df_long$Type=="GA"] <- "Gendered Activities"
df_long$Type[df_long$Type=="GFO"] <- "Gendered Family Organization"


data_plot <- split(df_long, df_long$Type)

my_plot <- function(dat) {
  
ggplot(data=dat, aes(x=Value, fill=sexe)) + geom_histogram(position="dodge", bins=20) + 
  scale_fill_manual(name="Sex",values=c( "#1F78B4","#A6CEE3"),
                    labels=c("Girls","Boys")) + xlab("Scaled score") + ylab("Count") +
  theme_bw(base_size=12)+
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) +
    theme(legend.position = "none")  
}

plots <- lapply(data_plot, my_plot)


plot_legend <- ggplot(df_long, aes(x=Value, fill=sexe)) + geom_histogram(position="dodge", bins=20) + 
  scale_fill_manual(name="Sex",values=c( "#1F78B4","#A6CEE3"),
                    labels=c("Girls","Boys")) + xlab("Scaled score") + ylab("Count") +
  theme_bw(base_size=12)+
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

grobs <- ggplotGrob(plot_legend)$grobs
legend <- grobs[[which(sapply(grobs, function(x) x$name) == "guide-box")]]

library(cowplot)
pgrid <- plot_grid(plots$`Gendered Activities`, plots$`Gendered Family Organization`, labels="AUTO")


# add row and column names

# Create empty plots for the labels
library(patchwork)
empty <- ggdraw() +
    draw_label("", x = 0.5, y = 0.5, fontface = "bold") +
    plot_layout(guides = "collect")
column_label_plot <- ggdraw() +
    draw_label("Gendered Activities", x = 0.5, y = 0.5, fontface = "bold") +
    plot_layout(guides = "collect")
column_label_plot2 <- ggdraw() +
    draw_label("Gendered Family Organization", x = 0.5, y = 0.5, fontface = "bold") +
    plot_layout(guides = "collect")

# Plot grid with labels for both columns and rows
pgrid <- plot_grid(plots$`Gendered Activities`, plots$`Gendered Family Organization`, labels="AUTO")
colname <- plot_grid(column_label_plot, column_label_plot2)
pgrid2 <- plot_grid(colname, pgrid, ncol=1, rel_heights = c(0.2, 1))
pgrid3 <- plot_grid(pgrid2, legend, ncol = 2, rel_widths = c(1, .1))
pgrid3
```


# Figure 2 : School scores distributions 

```{r}
df_long <- elfe_mids$data %>%
  pivot_longer(cols = c(scorenum6, scorenum4, scorelit6, scorelit4), 
               names_to = "Type",
               values_to = "Value")

df_long$Type[df_long$Type=="scorenum6"] <- "1st grade mathematics score"
df_long$Type[df_long$Type=="scorenum4"] <- "Preschool mathematics score"
df_long$Type[df_long$Type=="scorelit6"] <- "1st grade literacy score"
df_long$Type[df_long$Type=="scorelit4"] <- "Preschool literacy score"

data_plot <- split(df_long, df_long$Type)

my_plot <- function(dat) {
  
ggplot(data=dat, aes(x=Value, fill=sexe)) + geom_histogram(position="dodge", bins=20) + 
  scale_fill_manual(name="Sex",values=c( "#1F78B4","#A6CEE3"),
                    labels=c("Girls","Boys")) + xlab("Scaled score") + ylab("Count") +
  theme_bw(base_size=12)+
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()) +
    theme(legend.position = "none")  
}

plots <- lapply(data_plot, my_plot)


plot_legend <- ggplot(df_long, aes(x=Value, fill=sexe)) + geom_histogram(position="dodge", bins=20) + 
  scale_fill_manual(name="Sex",values=c( "#1F78B4","#A6CEE3"),
                    labels=c("Girls","Boys")) + xlab("Scaled score") + ylab("Count") +
  theme_bw(base_size=12)+
  theme(plot.background = element_blank(),
        panel.grid.major = element_blank(),
    panel.grid.minor = element_blank())

grobs <- ggplotGrob(plot_legend)$grobs
legend <- grobs[[which(sapply(grobs, function(x) x$name) == "guide-box")]]

library(cowplot)
pgrid <- plot_grid(plots$`Preschool mathematics score`, plots$`1st grade mathematics score`, plots$`Preschool literacy score`, plots$`1st grade literacy score`, labels="AUTO")
#plot_grid(pgrid, legend, ncol = 1, rel_widths = c(1, .1))


# add row and column names

# Create empty plots for the labels
library(patchwork)
empty <- ggdraw() +
    draw_label("", x = 0.5, y = 0.5, fontface = "bold") +
    plot_layout(guides = "collect")
column_label_plot <- ggdraw() +
    draw_label("Preschool", x = 0.5, y = 0.5, fontface = "bold") +
    plot_layout(guides = "collect")
column_label_plot2 <- ggdraw() +
    draw_label("1st grade", x = 0.5, y = 0.5, fontface = "bold") +
    plot_layout(guides = "collect")
row_label_plot <- ggdraw() +
    draw_label("Math", x = 0.5, y = 0.5, fontface = "bold", angle=90) +
    plot_layout(guides = "collect")
row_label_plot2 <- ggdraw() +
    draw_label("Literacy", x = 0.5, y = 0.5, fontface = "bold", angle=90) +
    plot_layout(guides = "collect")

# Plot grid with labels for both columns and rows
pgrid <- plot_grid(plots$`Preschool mathematics score`, plots$`1st grade mathematics score`, plots$`Preschool literacy score`, plots$`1st grade literacy score`, labels="AUTO")
colname <- plot_grid(column_label_plot, column_label_plot2)
pgrid2 <- plot_grid(colname, pgrid, ncol=1, rel_heights = c(0.2, 1))
rowname <- plot_grid(row_label_plot,row_label_plot2, ncol=1)
pgrid3 <- plot_grid(rowname, pgrid2, ncol=2, rel_widths = c(0.1, 1))
pgrid4 <- plot_grid(pgrid3, legend, ncol = 2, rel_widths = c(1, .1))
pgrid4


```


# 3/ Regressions for mathematics in 1st grade
 
```{r}

#creation of separate dataset for each school scores (num preschool and 1st grade, lit preschool and 1st grade)
test  <- complete(elfe_mids,"long",include=T)
test <- test[!is.na(test$scorenum4),]
elfe_mids_scorenum4 <- as.mids(test, .id="row")

test  <- complete(elfe_mids,"long",include=T)
test <- test[!is.na(test$scorelit4),]
elfe_mids_scorelit4 <- as.mids(test, .id="row")

test  <- complete(elfe_mids,"long",include=T)
test <- test[!is.na(test$scorelit6),]
elfe_mids_scorelit6 <- as.mids(test, .id="row")

test  <- complete(elfe_mids,"long",include=T)
test <- test[!is.na(test$scorenum6),]
elfe_mids_scorenum6 <- as.mids(test, .id="row")


```



##H1 all (table S4)
```{r}

reg1 <- with(elfe_mids_scorenum6, 
             lm(scale(scorenum6) ~ scale(GFO) + Sex + scale(GFO) * Sex + A5_TOTREVEN + meduc_5y + feduc_5y))


table1 <- tbl_regression(reg1, label=c(Sex ~ "Sex", 
                       #GFO ~ "Gendered Family Organization (GFO)",
                       
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A5_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))
table1



```

## Figure 4

```{r}
test <- complete(elfe_mids_scorenum6,"long",include=T)
data <- test[which(test$.imp==2),]

data_graph <- data
data_graph <- data_graph[!is.na(data_graph$GFO),]
data_graph$Quartiles <- cut(data_graph$GFO, breaks = quantile(data_graph$GFO, probs = 0:4/4, na.rm = TRUE), labels = FALSE, include.lowest = TRUE)
data_graph$scorenum6 <- scale(data_graph$scorenum6)


result <- data_graph %>%
  group_by(Quartiles, sexe) %>%
  summarize(mean_scorenum6 = mean(scorenum6)) %>% 
  pivot_wider(names_from = sexe, values_from = mean_scorenum6) %>%
  mutate(Difference = Garçons - Filles)

#### calculating 95 CI for the difference boys-girls
CI  <- data_graph %>%
    group_by(Quartiles, sexe) %>%
    summarize(mean_scorenum6 = mean(scorenum6),sd=sd(scorenum6), N=n())
pooled_var <- c(      # sp2 = ((n1-1)s12 + (n2-1)s22) / (n1+n2-2)
  ((CI$N[CI$Quartiles==1 & CI$sexe=="Garçons"]-1)*CI$sd[CI$Quartiles==1 & CI$sexe=="Garçons"]**2 + (CI$N[CI$Quartiles==1 & CI$sexe=="Filles"]-1)*CI$sd[CI$Quartiles==1 & CI$sexe=="Filles"]**2 )/(CI$N[CI$Quartiles==1 & CI$sexe=="Filles"]+CI$N[CI$Quartiles==1 & CI$sexe=="Garçons"]-2),
  
  ((CI$N[CI$Quartiles==2 & CI$sexe=="Garçons"]-1)*CI$sd[CI$Quartiles==2 & CI$sexe=="Garçons"]**2 + (CI$N[CI$Quartiles==2 & CI$sexe=="Filles"]-1)*CI$sd[CI$Quartiles==2 & CI$sexe=="Filles"]**2 )/(CI$N[CI$Quartiles==2 & CI$sexe=="Filles"]+CI$N[CI$Quartiles==2 & CI$sexe=="Garçons"]-2),
  
  ((CI$N[CI$Quartiles==3 & CI$sexe=="Garçons"]-1)*CI$sd[CI$Quartiles==3 & CI$sexe=="Garçons"]**2 + (CI$N[CI$Quartiles==3 & CI$sexe=="Filles"]-1)*CI$sd[CI$Quartiles==3 & CI$sexe=="Filles"]**2 )/(CI$N[CI$Quartiles==3 & CI$sexe=="Filles"]+CI$N[CI$Quartiles==3 & CI$sexe=="Garçons"]-2),
  
  ((CI$N[CI$Quartiles==4 & CI$sexe=="Garçons"]-1)*CI$sd[CI$Quartiles==4 & CI$sexe=="Garçons"]**2 + (CI$N[CI$Quartiles==4 & CI$sexe=="Filles"]-1)*CI$sd[CI$Quartiles==4 & CI$sexe=="Filles"]**2 )/(CI$N[CI$Quartiles==4 & CI$sexe=="Filles"]+CI$N[CI$Quartiles==4 & CI$sexe=="Garçons"]-2)
  
)

MOE <- data.frame(Quartiles=c(1,2,3,4), 
                     MOE=c(
                       1.96*sqrt(pooled_var[1]/CI$N[CI$Quartiles==1 & CI$sexe=="Garçons"] + pooled_var[1]/CI$N[CI$Quartiles==1 & CI$sexe=="Filles"]),
                       
                       1.96*sqrt(pooled_var[1]/CI$N[CI$Quartiles==2 & CI$sexe=="Garçons"] + pooled_var[1]/CI$N[CI$Quartiles==2 & CI$sexe=="Filles"]),
                       
                       1.96*sqrt(pooled_var[1]/CI$N[CI$Quartiles==3 & CI$sexe=="Garçons"] + pooled_var[1]/CI$N[CI$Quartiles==3 & CI$sexe=="Filles"]),
                       
                       1.96*sqrt(pooled_var[1]/CI$N[CI$Quartiles==4 & CI$sexe=="Garçons"] + pooled_var[1]/CI$N[CI$Quartiles==4 & CI$sexe=="Filles"])
                       ))

result <- cbind(result, MOE=MOE$MOE)

### plot # 
 library(RColorBrewer)

ggplot(result, aes(x = as.factor(Quartiles), y = Difference, fill = as.factor(Quartiles))) +
  geom_bar(stat = "identity") +
  labs(
       x = "GFO quartile",
       y = "Boys/Girls Math Score Difference") +
  scale_x_discrete( labels=c("First ", "Second ", "Third ", "Fourth ")) +
  scale_fill_manual(values = c("thistle","#B2DF8A" ,"#FB9A99" , "#FDBF6F")) +
  guides(fill="none") +
  theme_minimal() +
  theme(panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.title.x = element_text(size=12),
           axis.text.x  = element_text(size=11),
        axis.title.y = element_text(size=12),
           axis.text.y  = element_text(size=11),
        legend.title= element_text(size=12,colour="black"),
        legend.text= element_text(size=10)) +
  geom_errorbar(aes(ymin = Difference-MOE, ymax = Difference+MOE,color = as.factor(Quartiles)), width=0.2) +
  scale_color_manual(values = c("darkslateblue","#33A02C" , "#E31A1C" , "#FF7F00")) +
  guides(color="none")  + theme(text = element_text(size=13)) 
```


##Post-hoc H1 by sex (table S6)
```{r}

test  <- complete(elfe_mids_scorenum6,"long",include=T)
test_girls <- test[test$Sex==0.5,]
test_boys<- test[test$Sex==-0.5,]
girls_mids <- as.mids(test_girls, .id="row")
boys_mids <- as.mids(test_boys, .id="row")

#girls
reg1_g <- with(girls_mids, 
             lm(scale(scorenum6) ~ scale(GFO) + A5_TOTREVEN + meduc_5y + feduc_5y))
# boys
reg1_b <- with(boys_mids, 
             lm(scale(scorenum6) ~ scale(GFO) + A5_TOTREVEN + meduc_5y + feduc_5y))


table1_g <- tbl_regression(reg1_g, label=c(
                       #GFO ~ "Gendered Family Organization (GFO)",
                       
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A5_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))

table1_b <- tbl_regression(reg1_b, label=c( 
                       #GFO ~ "Gendered Family Organization (GFO)",
                       
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A5_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))

tbl_merge(list(table1_g, table1_b), tab_spanner = c( "**Girls**", "**Boys**"))


```



##H2 all (table S7)

```{r results='asis'}
reg2 <- with(elfe_mids_scorenum6,
             lm( scale(GA) ~  scale(GFO) + Sex +  scale(GFO) * Sex + A5_TOTREVEN + meduc_5y + feduc_5y))

table2 <- tbl_regression(reg2, label=c(Sex ~ "Sex", 
                       #GFO ~ "Gendered Family Organization (GFO)",
                       
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A5_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))
table2


```

### GAC (tables S8 and S9)

```{r}
test  <- complete(elfe_mids_scorenum6,"long",include=T)
test$GAC <- test$GA
test$GAC[test$Sex==0.5] <- -test$GA[test$Sex==0.5]
elfe_mids_scorenum6_GAC <- as.mids(test, .id="row")

reg2_GAC <- with(elfe_mids_scorenum6_GAC,
             lm( scale(GAC) ~  scale(GFO) + Sex +  scale(GFO) * Sex + A5_TOTREVEN + meduc_5y + feduc_5y))

table2_GAC <- tbl_regression(reg2_GAC, label=c(Sex ~ "Sex", 
                       #GFO ~ "Gendered Family Organization (GFO)",
                       
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A5_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))
table2_GAC



### boys girls separately

test  <- complete(elfe_mids_scorenum6_GAC,"long",include=T)
test_girls <- test[test$Sex==0.5,]
test_boys<- test[test$Sex==-0.5,]
girls_mids <- as.mids(test_girls, .id="row")
boys_mids <- as.mids(test_boys, .id="row")

#girls
reg_gac_g <- with(girls_mids, 
             lm( scale(GAC) ~  scale(GFO)  + A5_TOTREVEN + meduc_5y + feduc_5y))
# boys
reg_gac_b <- with(boys_mids, 
             lm( scale(GAC) ~  scale(GFO)  + A5_TOTREVEN + meduc_5y + feduc_5y))


table_gac_g <- tbl_regression(reg_gac_g, label=c(
                       #GFO ~ "Gendered Family Organization (GFO)",
                       
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A5_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))

table_gac_b <- tbl_regression(reg_gac_b, label=c( 
                       #GFO ~ "Gendered Family Organization (GFO)",
                       
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A5_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))

tbl_merge(list(table_gac_g, table_gac_b), tab_spanner = c( "**Girls**", "**Boys**"))
```

### Figure 5

```{r}
test <- complete(elfe_mids_scorenum6_GAC,"long",include=T)
data_GAC <- test[which(test$.imp==1),]


test_H2_GAC <- lm(scale(GAC)~ GFO + Sex + GFO * Sex +  meduc_5y + feduc_5y + A5_TOTREVEN, data=data_GAC)
plot_H2_GAC <- interact_plot(test_H2_GAC, pred = GFO, interval = T, partial.residuals = F, modx = Sex, colors = c("#A6CEE3", "#1F78B4"), modx.labels = c("Boys", "Girls"), y.label = "Gendered Activity Congruency", x.label="Gendered Family Organization") + theme(text = element_text(size=15))
plot_H2_GAC

```




## H3 - Médiation : 

Sobel test 
```{r}
library(powerMediation)
test  <- complete(elfe_mids,"long",include=T)
test <- test[!is.na(test$scorenum6),]
elfe_mids_scorenum6 <- as.mids(test, .id="row")


regtotal = with(elfe_mids_scorenum6, lm(scale(scorenum6) ~ Sex + scale(GA) + meduc_5y + A5_TOTREVEN + feduc_5y))
regmediated = with(elfe_mids_scorenum6, lm(scale(GA) ~ Sex +  meduc_5y + A5_TOTREVEN + feduc_5y))
total <- summary(pool(regtotal))
mediated <- summary(pool(regmediated))

testMediation.Sobel(mediated$estimate[2], 
                    total$estimate[3],
                    mediated$std.error[2]*sqrt(nobs(regmediated[["analyses"]][[1]])),
                    total$std.error[3]*sqrt(nobs(regtotal[["analyses"]][[1]])) )

indirectGA <- mediated$estimate[2]*total$estimate[3]
indirectGA

```


##H4 all (table S10)

```{r results='asis'}

reg4 <- with(elfe_mids_scorenum6,
             lm(scale(scorenum6) ~ Sex +  scale(GFO) +  scale(GFO) * Sex +  scale(GA) + A5_TOTREVEN + meduc_5y + feduc_5y))

table3 <- tbl_regression(reg4, label=c(Sex ~ "Sex", 
                       #GFO ~ "Gendered Family Organization (GFO)",
                       #GA ~ "Gendered Activities (GA)",
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A5_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))
table3

```




# 4/ For Lit 1st Grade + preschool, and Num preschool


## H1 (table S5)

```{r}

### num4

reg5 <- with(elfe_mids_scorenum4, 
             lm(scale(scorenum4) ~  scale(GFO) + Sex +  scale(GFO) * Sex + A3_TOTREVEN + meduc_5y + feduc_5y))


table1_num4 <- tbl_regression(reg5, label=c(Sex ~ "Sex", 
                       #GFO ~ "Gendered Family Organization (GFO)",
                       
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A3_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))


### lit6
reg9 <- with(elfe_mids_scorelit6, 
             lm( scale(scorelit6) ~  scale(GFO) + Sex +  scale(GFO) * Sex + A5_TOTREVEN + meduc_5y+ feduc_5y))


table1_lit6 <- tbl_regression(reg9, label=c(Sex ~ "Sex", 
                       #GFO ~ "Gendered Family Organization (GFO)",
                       
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A5_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))


### lit4
reg13 <- with(elfe_mids_scorelit4, 
             lm( scale(scorelit4) ~  scale(GFO) + Sex +  scale(GFO) * Sex + A3_TOTREVEN + meduc_5y + feduc_5y))


table1_lit4 <- tbl_regression(reg13, label=c(Sex ~ "Sex", 
                      # GFO ~ "Gendered Family Organization (GFO)",
                       
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A3_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))



tbl_merge(list(table1_num4, table1_lit4, table1_lit6), tab_spanner = c("**Mathematics preschool**","**Literacy preschool**", "**Literacy 1st grade**"))




```

## Figure 3

```{r}
### num4 old colors c("red3", "magenta4")
test <- complete(elfe_mids_scorenum4,"long",include=T)
data_scorenum4 <- test[which(test$.imp==2),]
data_scorenum4$GFO <- scale(data_scorenum4$GFO)

test_H1_num4 <- lm(scale(scorenum4) ~ GFO + Sex + GFO * Sex +  meduc_5y + feduc_5y + A3_TOTREVEN, data=data_scorenum4)
plot_H1_num4 <- interact_plot(test_H1_num4, pred = GFO, interval = T, partial.residuals = F, modx = Sex, colors = c("#A6CEE3", "#1F78B4"), modx.labels = c("Boys", "Girls"), y.label = "PS math test score", legend.main = "Sex")  +coord_cartesian(ylim = c(-0.4, 0.4)) +     theme_classic() + xlab("") + theme(legend.position = "none") + ylab("Score") + theme(text = element_text(size=13))


### num 6
test <- complete(elfe_mids_scorenum6,"long",include=T)
data <- test[which(test$.imp==2),]
data$GFO <- scale(data$GFO)
test_H1_num6 <- lm(scale(scorenum6) ~ GFO + Sex + GFO*Sex +  meduc_5y + feduc_5y + A5_TOTREVEN, data=data)
plot_H1_num6 <- interact_plot(test_H1_num6, pred = GFO, interval = T, partial.residuals = F, modx = Sex, colors = c("#A6CEE3", "#1F78B4"), modx.labels = c("Boys", "Girls"), y.label = "1st grade math test score", legend.main = "Sex") +coord_cartesian(ylim = c(-0.4, 0.4)) +     theme_classic() + xlab("") + theme(legend.position = "none")    + ylab("")  + theme(text = element_text(size=13)) 


### lit6
test <- complete(elfe_mids_scorelit6,"long",include=T)
data_scorelit6 <- test[which(test$.imp==2),]
data_scorelit6$GFO <- scale(data_scorelit6$GFO)

test_H1_lit6 <- lm(scale(scorelit6) ~ GFO + Sex + GFO * Sex +  meduc_5y + feduc_5y + A5_TOTREVEN, data=data_scorelit6)
plot_H1_lit6 <- interact_plot(test_H1_lit6, pred = GFO, interval = T, partial.residuals = F, modx = Sex, colors = c("#A6CEE3", "#1F78B4"), modx.labels = c("Boys", "Girls"), y.label = "1st grade literacy test score", legend.main = "Sex") +coord_cartesian(ylim = c(-0.4, 0.4)) +     theme_classic() + theme(legend.position = "none")  + ylab("")  + xlab("Gendered Family Organization")   + theme(text = element_text(size=13))
#+ labs(x = expression(paste(italic("More traditional"), "\u2190", "       Gendered Family Organization     ", "\u2192", italic("Less traditional"))) ) 

### lit4
test <- complete(elfe_mids_scorelit4,"long",include=T)
data_scorelit4 <- test[which(test$.imp==2),]
data_scorelit4$GFO <- scale(data_scorelit4$GFO)

test_H1_lit4 <- lm(scale(scorelit4) ~ GFO + Sex + GFO * Sex +  meduc_5y + feduc_5y + A3_TOTREVEN, data=data_scorelit4)
plot_H1_lit4 <- interact_plot(test_H1_lit4, pred = GFO, interval = T, partial.residuals = F, modx = Sex, colors = c("#A6CEE3", "#1F78B4"), modx.labels = c("Boys", "Girls"), y.label = "PS literacy test score", legend.main = "Sex")  +coord_cartesian(ylim = c(-0.4, 0.4)) +     theme_classic() + theme(legend.position = "none") + ylab("Score")  + xlab("Gendered Family Organization")   + theme(text = element_text(size=13))


# adding legend and plot together
plot_legend <- interact_plot(test_H1_lit4, pred = GFO, interval = T, partial.residuals = F, modx = Sex, colors = c("#A6CEE3", "#1F78B4"), modx.labels = c("Boys", "Girls"), y.label = "PS literacy test score", legend.main = "Sex")  +coord_cartesian(ylim = c(-0.4, 0.4)) +     theme_classic() #+ theme (legend.position="bottom") 
grobs <- ggplotGrob(plot_legend)$grobs
legend <- grobs[[which(sapply(grobs, function(x) x$name) == "guide-box")]]

library(cowplot)
pgrid <- plot_grid(plot_H1_num4, plot_H1_num6, plot_H1_lit4, plot_H1_lit6, labels="AUTO")
#plot_grid(pgrid, legend, ncol = 1, rel_widths = c(1, .1))


# add row and column names

# Create empty plots for the labels

empty <- ggdraw() +
    draw_label("", x = 0.5, y = 0.5, fontface = "bold") +
    plot_layout(guides = "collect")
column_label_plot <- ggdraw() +
    draw_label("Preschool", x = 0.5, y = 0.5, fontface = "bold") +
    plot_layout(guides = "collect")
column_label_plot2 <- ggdraw() +
    draw_label("1st grade", x = 0.5, y = 0.5, fontface = "bold") +
    plot_layout(guides = "collect")
row_label_plot <- ggdraw() +
    draw_label("Math", x = 0.5, y = 0.5, fontface = "bold", angle=90) +
    plot_layout(guides = "collect")
row_label_plot2 <- ggdraw() +
    draw_label("Literacy", x = 0.5, y = 0.5, fontface = "bold", angle=90) +
    plot_layout(guides = "collect")

# Plot grid with labels for both columns and rows
pgrid <- plot_grid(plot_H1_num4, plot_H1_num6, plot_H1_lit4, plot_H1_lit6, labels="AUTO")
colname <- plot_grid(column_label_plot, column_label_plot2)
pgrid2 <- plot_grid(colname, pgrid, ncol=1, rel_heights = c(0.2, 1))
rowname <- plot_grid(row_label_plot,row_label_plot2, ncol=1)
pgrid3 <- plot_grid(rowname, pgrid2, ncol=2, rel_widths = c(0.1, 1))
pgrid4 <- plot_grid(pgrid3, legend, ncol = 2, rel_widths = c(1, .1))
pgrid4

```



## H3
Sobel tests
p>0.9 for all

### Num preschool
```{r}
library(powerMediation)

test  <- complete(elfe_mids,"long",include=T)
test <- test[!is.na(test$scorenum4),]
elfe_mids_scorenum4 <- as.mids(test, .id="row")


regtotal = with(elfe_mids_scorenum4, lm(scale(scorenum4) ~ Sex + scale(GA) + meduc_5y + A3_TOTREVEN + feduc_5y))
regmediated = with(elfe_mids_scorenum4, lm(scale(GA) ~ Sex +  meduc_5y + A3_TOTREVEN + feduc_5y))
total <- summary(pool(regtotal))
mediated <- summary(pool(regmediated))

testMediation.Sobel(mediated$estimate[2], 
                    total$estimate[3],
                    mediated$std.error[2]*sqrt(nobs(regmediated[["analyses"]][[1]])),
                    total$std.error[3]*sqrt(nobs(regtotal[["analyses"]][[1]])) )

indirectGA <- mediated$estimate[2]*total$estimate[3]
indirectGA

```

### Lit preschool
```{r}
test  <- complete(elfe_mids,"long",include=T)
test <- test[!is.na(test$scorelit4),]
elfe_mids_scorelit4 <- as.mids(test, .id="row")


regtotal = with(elfe_mids_scorelit4, lm(scale(scorelit4) ~ Sex + scale(GA) + meduc_5y + A3_TOTREVEN + feduc_5y))
regmediated = with(elfe_mids_scorelit4, lm(scale(GA) ~ Sex +  meduc_5y + A3_TOTREVEN + feduc_5y))
total <- summary(pool(regtotal))
mediated <- summary(pool(regmediated))

testMediation.Sobel(mediated$estimate[2], 
                    total$estimate[3],
                    mediated$std.error[2]*sqrt(nobs(regmediated[["analyses"]][[1]])),
                    total$std.error[3]*sqrt(nobs(regtotal[["analyses"]][[1]])) )

indirectGA <- mediated$estimate[2]*total$estimate[3]
indirectGA

```

### Lit 1st grade 
```{r}

test  <- complete(elfe_mids,"long",include=T)
test <- test[!is.na(test$scorelit6),]
elfe_mids_scorelit6 <- as.mids(test, .id="row")


regtotal = with(elfe_mids_scorelit6, lm(scale(scorelit6) ~ Sex + scale(GA) + meduc_5y + A5_TOTREVEN + feduc_5y))
regmediated = with(elfe_mids_scorelit6, lm(scale(GA) ~ Sex +  meduc_5y + A5_TOTREVEN + feduc_5y))
total <- summary(pool(regtotal))
mediated <- summary(pool(regmediated))

testMediation.Sobel(mediated$estimate[2], 
                    total$estimate[3],
                    mediated$std.error[2]*sqrt(nobs(regmediated[["analyses"]][[1]])),
                    total$std.error[3]*sqrt(nobs(regtotal[["analyses"]][[1]])) )

indirectGA <- mediated$estimate[2]*total$estimate[3]
indirectGA

```


## H4 (table S11)

```{r}





## num4
reg4num4 <- with(elfe_mids_scorenum4,
             lm( scale(scorenum4) ~ Sex +  scale(GFO) +  scale(GFO) * Sex +  scale(GA) + A3_TOTREVEN + meduc_5y + feduc_5y))

table3_num4 <- tbl_regression(reg4num4, label=c(Sex ~ "Sex", 
                       #GFO ~ "Gendered Family Organization (GFO)",
                       #GA ~ "Gendered Activities (GA)",
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A3_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))


### lit4
reg4lit4 <- with(elfe_mids_scorelit4,
             lm( scale(scorelit4) ~ Sex +  scale(GFO) +  scale(GFO) * Sex +  scale(GA) + A3_TOTREVEN + meduc_5y + feduc_5y))

table3_lit4 <- tbl_regression(reg4lit4, label=c(Sex ~ "Sex", 
                       #GFO ~ "Gendered Family Organization (GFO)",
                       #GA ~ "Gendered Activities (GA)",
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A3_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))

### lit6
reg4lit6 <- with(elfe_mids_scorelit6,
             lm( scale(scorelit6) ~ Sex +  scale(GFO) +  scale(GFO) * Sex +  scale(GA) + A5_TOTREVEN + meduc_5y+ feduc_5y))

table3_lit6 <- tbl_regression(reg4lit6, label=c(Sex ~ "Sex", 
                       #GFO ~ "Gendered Family Organization (GFO)",
                       #GA ~ "Gendered Activities (GA)",
                       meduc_5y ~ "Mother's education ",
                       feduc_5y ~ "Father's education ",
                       A5_TOTREVEN ~ "Household’s monthly income at 5 years (€)"))


tbl_merge(list(table3_num4, table3_lit4,table3_lit6  ), tab_spanner = c( "**Mathematics preschool**", "**Literacy preschool**","**Literacy 1st grade**" ))
```

